The ideal choice of an abstraction partition is the one that balances well the trade-off between precision and size. More precisely, the abstraction should be precise enough to give enough power to the agent to satisfy its surveillance objective. An abstraction that is too precise, however often results in an infeasibly large state-space of the resulting game. Thus, a good abstraction is one that gives the right level of precision where it is needed, and is coarse (that is, generates fewer abstract belief states) where precision is not needed. Thus, choosing a good abstraction partition is often specific to the game environment and the surveillance specification. In section \ref{sec:experiments}, we present  examples with user specified partitions resulting in feasible  abstract games.

In the previous section we discussed that a winning strategy for the agent in the abstract belief game corresponds to a strategy for the agent in the concrete belief game. This, however is not in general true for the abstract winning strategies of the target. We refer to the abstract winning  strategies for the target as \emph{abstract counterexamples}.

Given an abstract counterexample, there are two possibilities: it can either be a counterexample in the concrete belief game, meaning that the agent cannot satisfy the surveillance objective, or it can result from the coarseness of the abstraction partition. We now discuss in more detail counterexamples in safety and liveness surveillance games . The latter generalize also to general surveillance objectives.
