In the construction of the abstract  game structure, we overapproximate the belief-set of the agent at each step. Since we consider surveillance predicates that impose upper bounds on the size of the belief, such an abstraction  gives more power to the target (and, dually less power to the agent).  This construction guarantees that the abstraction is \emph{sound}, meaning that an abstract strategy for the agent that achieves a surveillance objective corresponds to a winning strategy in the concrete game. This is stated in the following theorem.

\begin{theorem}
Let $G$ be a surveillance game structure, $\part = \{Q_i\}_{i=1}^n$ be an abstraction partition, and $G_\abstr = \alpha_\part(G)$. For every surveillance objective $\varphi$, if there exists a wining strategy for the agent in the abstract belief-set game $(\alpha_\part(G),\varphi)$, then there exists a winning strategy for the agent in the concrete surveillance game $(G,\varphi)$.
\end{theorem}

\paragraph{Choosing an abstraction partition} Choosing an 'appropriate' partition can result in a controller that can guarantee the surveillance specifications with fewer abstract belief states. However, choosing the abstraction partition is, in general, specific to the game environment. In section \ref{sec:experiments}, we present some examples with user specified partitions. If the abstraction is too coarse, the user can refine the abstract states with the help of counterexamples. The nature of these counterexamples for the classes of surveillance specifications presented in this papers are defined in the next section.

The refinement procedure can be automated (CEGAR), however, for space constraints we do not include the details in this paper. 